### 2021-01-22 proposals/TESS_GI_cycle04/tessgi_gully_cycle4.tex
Getting sorta mathy here, not sure that is a good thing

\textbf{Kepler and TESS perceive different starspot contrasts.}

@@

System-throughput-weighted contrast spectra can be integrated over the illustrated filter curves to yield precision estimates for contrasts in the two passbands.  For this M0V example, we obtain $c_{\ktwo}\sim0.025$ and $c_{\tess}\sim0.1$.  Starspots appear about four times darker in \kepler\ and \ktwo\ than they do in \tess.  We define the ratio of starspot contrasts of \tess\ compared to \kepler\ as $\mathcal{R}\equiv \frac{c_{\tess}}{c_{\ktwo}}$.  This proposal will systematically measure $\mathcal{R}$ for a vast number of stars observed by both missions.

\textbf{Spot-induced modulation amplitudes depend on contrast.}
Rotationally-modulated lightcurves exhibit semi-sinusoidal undulations as starspots (or spot groups) enter and exit the projected stellar disk.  The most-spotted projected hemisphere is directed towards the observer at the moment of the lightcurve minimum, and the least-spotted projected hemisphere at lightcurve maximum.  The amplitude of the lightcurve, therefore, equals the difference in starspot coverage fractions $\Delta f_{spot} \equiv f_{max}-f_{min}$ between the most-and-least spotted projected hemispheres weighted by the spot contrast: $ A_\lambda = \Delta f_{spot} \cdot (1-c_\lambda)$.  Therefore the ratio of \tess\ to \kepler\ amplitudes yields a constraint independent of the actual spot coverage fraction:

@@

Recent stellar surface inhomogeneity modeling \cite{2018ApJ...853..122R, 2018ApJ...868..143G, 2018ApJ...865..142B} has yielded coarse scaling factors $\zeta$ for estimating the total starspot surface coverage fraction from the observed lightcurve amplitude $f_{spot}$, yielding $ p(f_{spot}) = \zeta \cdot A $, where $\zeta$ represents a probability distribution with values typically between 1 and 50, depending on the degree of assumed starspot longitudinal symmetry.  Equipped solely with \tess-measured lightcurve amplitudes, we can provide what practitioners seek: a per-star estimate of $f_{spot}$ and $T_{spot}$.

\textbf{Head-to-head comparison of K2 and TESS amplitudes in the ecliptic fields}

@@

The main two factors that affect spot-modulation lightcurve amplitudes are effective temperature (\emph{i.e.} mass), and rotation period (\emph{i.e.} stellar activity/magnetic fields) \cite{2014ApJS..211...24M}.  Other important-albeit-unknown factors like stellar inclination angle and multiplicity are statistically identical between the \tess\ and \kepler\ samples.  We, therefore, propose to follow \cite{2014ApJS..211...24M} by constructing plots of amplitude versus period, subdivided into bins of effective temperature.  The two samples should look identical in these plots, but the locus of \tess\ sources is expected to fall below the \kepler\ sample, as in panel D of Figure \ref{fig:predictAmps}.

>>>>

\noindent\textbf{Kepler and TESS perceive different starspot contrasts.}

@@

System-throughput-weighted contrast spectra can be integrated over the illustrated filter curves to yield precision estimates for contrasts in the two passbands.  For this M0V example, we obtain $c_{\ktwo}\sim0.025$ and $c_{\tess}\sim0.1$.  Starspots appear about four times darker in \kepler\ and \ktwo\ than they do in \tess.  We define the ratio of starspot contrasts of \tess\ compared to \kepler\ as $\mathcal{R}\equiv \frac{c_{\tess}}{c_{\ktwo}}$.  This proposal will systematically measure $\mathcal{R}$ for a vast number of stars observed by both missions.
\newline

\noindent \textbf{Spot-induced modulation amplitudes depend on contrast.}

Rotationally-modulated lightcurves exhibit semi-sinusoidal undulations as starspots (or spot groups) enter and exit the projected stellar disk.  The most-spotted projected hemisphere is directed towards the observer at the moment of the lightcurve minimum, and the least-spotted projected hemisphere at lightcurve maximum.  The amplitude of the lightcurve, therefore, is approximately the difference in starspot coverage fractions $\Delta f_{spot} \equiv f_{max}-f_{min}$ between the most-and-least spotted projected hemispheres, weighted by the spot contrast: $ A_\lambda = \Delta f_{spot} \cdot (1-c_\lambda)$.  Therefore the ratio of \tess\ to \kepler\ amplitudes yields a constraint independent of the actual spot coverage fraction:

@@

The notation is cumbersome, but the takeaway is clear: \textbf{we can quantify spot contrast ratio knowing only the amplitudes of \ktwo\ and \tess\ spot-modulated lightcurves.}  This equation is approximate, and in practice our team will derive $\mathcal{R}= \frac{c_{\tess}}{c_{\ktwo}}$ with Monte Carlo methods to take into account the uncertainty of the amplitude determination and subtle starspot self-dilution effects.
\newline

\noindent \textbf{Head-to-head comparison of K2 and TESS amplitudes in the ecliptic fields}

@@

The main two factors that affect spot-modulation lightcurve amplitudes are effective temperature (\emph{i.e.} mass), and rotation period (\emph{i.e.} stellar activity/magnetic fields) \cite{2014ApJS..211...24M}.  Other important-albeit-unknown factors like stellar inclination angle and multiplicity \emph{cancel out} when we compare the same stars head-to-head.  We, therefore, propose to follow \cite{2014ApJS..211...24M} by constructing plots of amplitude versus period, subdivided into bins of effective temperature.  The two samples should look identical in these plots, but the locus of \tess\ sources is expected to fall below the \kepler\ sample, as in Figure \ref{fig:expected}.
